Visualization of [fulle name] Fractional Integrals

### 2019-05-27 fractional/CMJ style files/article-template.tex
added lit

\noindent
The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
of theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876}. Fractional calculus has now developed into a mature discipline \cite{machado14}. 
However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability. At the first international conference on fractional calculus in
New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}. Subsequently, the last few decades has seen 
a number of papers that attempt to rectify this. There now exists probabilistic interpretations, geometric interpretations, physical interpretations and ecenomic 
interpretations of fractional order integrals and differentials.

In this article we specifically focus on the geometric interpretation of fractional integrals. To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral.
As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
the Riemann-Lioville fractional integral. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
We, however, do not discuss them any further in this article. Investigating whether one can apply the proposed framework to other fractional integral definitions will be adressed in a 
future endeavour.

@@

\bibitem{davis59} Davis,~P.~J. (1959). "Leonhard Euler's Integral: A Historical Profile of the Gamma Function". \textit{Amer. Math. Monthly}. 66(10): 849--869

@@

@@

>>>>

\noindent
The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
of theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876,laurent1884}. Fractional calculus has now developed into a mature discipline \cite{machado14}. 
However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability. At the first international conference on fractional calculus in
New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}. Subsequently, the last few decades has seen 
a number of papers that attempt to rectify this. There now exists probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95} and economic 
interpretations \cite{tarasova17} of fractional order integrals and differentials.\\

\noindent
In this article we specifically focus on the geometric interpretation of fractional integrals. To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral \cite{laurent1884}.
As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
the Riemann-Liouville fractional integral \cite{laurent1884}. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
We, however, do not discuss them any further in this article. Investigating whether one can apply the proposed framework to other fractional integral definitions will be adressed in a 
future endeavour.

@@

\bibitem{davis59} Davis,~P.~J. (1959). Leonhard Euler's Integral: A Historical Profile of the Gamma Function. \textit{Amer. Math. Monthly}. 66(10): 849--869

@@

%Probability
\bibitem{stanislavsky04} Stanislavsky,~A.~A. (2004).  Probability interpretation of the integral of fractional order, \textit{Theoretical and Mathematical Physics.} 138(3): 418--431.

\bibitem{machado03} Machado,~J.~T. (2003). A probabilistic interpretation of the fractional-order differentiation. \textit{Fract. Calc. Appl. Anal.} 6(1): 73--80.

\bibitem{adda97} Adda,~F.~B. (1997). Geometric interpretation of the fractional derivative. \textit{Journal of Fract. Calc.}, 11: 21--52.

%Geometric
\bibitem{tarasov16} Tarasov,~V.~E. (2016). Geometric interpretation of fractional-order derivative. \textit{Fract. Calc. Appl. Anal.} 19(5): 1200--1221.

\bibitem{podlubny02} Podlubny,~I. (2002). Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \textit{Fract. Calc. Appl. Anal.} 5(4): 367--386.

%Physical
\bibitem{cioc16} Cioc, R. (2016). Physical and geometrical interpretation of Gr\"{u}nwald-Letnikov differintegrals: Measurement of path and acceleration. \textit{Fract. Calc. Appl. Anal.} 19(1): 161--172.

\bibitem{rutman95} Rutman,~R.S. (1995). On physical interpretations of fractional integration and differentiation. \textit{Theoretical and Mathematical Physics.} 105(3):1509--1519

%Economic
\bibitem{tarasova17} Tarasova,~V.~V., Tarasov,~V.~E. (2017). Economic Interpretation of Fractional Derivatives. \textit{Progress in Fractional Differentiation and Applications.} 3(1):1--7.

@@

\bibitem{laurent1884} Laurent, H. (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} 3(3):240--252.
